---
title: "Changes in UK mobility on EURO 2020 match days"
author: "Amber Barton"
date: "06/07/2021"
output: html_document
---

## Rationale

To find the extent to which concerns that crowds of fans celebrating EURO 2020 will facilitate spread of the SARS-CoV-2 variant are founded.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Results

**Retail and recreation**

Mobility for retail and recreation was markedly increased in certain areas of Scotland and Northern Ireland, and as would be expected, in Brent, the London Borough containing Wembley.

```{r echo = F, fig.width = 12}
library(ggplot2)
library(gridExtra)
library(grid)
load(file = "FootballGraphs.Rdata")
a = a + ggtitle("United Kingdom")
d = d + ggtitle("London")
grid.arrange(a, d, ncol = 2)
```

**Transit stations**

Mobility through transit stations was increased in certain areas of Scotland, in Brent and in Wrexham. 

```{r echo = F, fig.width = 12}
b = b + ggtitle("United Kingdom")
e = e + ggtitle("London")
grid.arrange(b, e, ncol = 2)
```

**Work place**

While England saw an increase in mobility to the work place, this was less the case in Scotland. 

```{r echo = F, fig.width = 12}
c = c + ggtitle("United Kingdom")
f = f + ggtitle("London")
grid.arrange(c, f, ncol = 2)
```


## Method

```{r pressure, echo=FALSE, fig.width = 4, fig.height = 3}
library(DiagrammeR)
grViz("digraph flowchart {
      # node definitions with substituted label text
      node [fontname = Helvetica, shape = rectangle]        
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']

      # edge definitions with the node IDs
      tab1 -> tab2 -> tab3 -> tab4 -> tab5;
      }

      [1]: 'Downloaded Google Community Mobility Reports up to June'
      [2]: 'Identified UK-based Euro Match Days'
      [3]: 'Normalised each to mobility on the previous 4 days of the same weekday'
      [4]: 'Took the mean of the normalised change in mobility for the match days'
      [5]: 'Merged with county boundary data from Open Geography Portal'
      ")
```

## Caveats

- Data is not available for July, where any effects would be more marked due to semi-finals and finals in Wembley

- Data provided was in the format of "percentage change from baseline", without providing baseline mobility figures

- Counties with lower populations could be more subject to random fluctuations in mobility
